---
title: "using loops for market analysis"
author: "D A Trading"
date: "5/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Getting a table of t-test results 
1. without using "for loop"
2. with "for loop"

NOTE: Pre-load NSDQmth object

```{r}
# t-test by decade
# 2010-2019
JultoOct2010 <- NSDQmth %>% 
  filter(month %in% c(7:10),
         decade == "2010-2019") 

NovtoJun2010 <- NSDQmth %>% 
  filter(month %in% c(1:6, 11, 12),
         decade == "2010-2019")

test2010 <- t.test(NovtoJun2010$perc_close, JultoOct2010$perc_close, alternative = "less")

# 2000-2009
JultoOct2000 <- NSDQmth %>% 
  filter(month %in% c(7:10),
         decade == "2000-2009") 

NovtoJun2000 <- NSDQmth %>% 
  filter(month %in% c(1:6, 11, 12),
         decade == "2000-2009")

test2000 <- t.test(NovtoJun2000$perc_close, JultoOct2000$perc_close, alternative = "less")

# 1990-1999
JultoOct1990 <- NSDQmth %>% 
  filter(month %in% c(7:10),
         decade == "1990-1999") 

NovtoJun1990 <- NSDQmth %>% 
  filter(month %in% c(1:6, 11, 12),
         decade == "1990-1999")

test1990 <- t.test(NovtoJun1990$perc_close, JultoOct1990$perc_close, alternative = "less")

# 1980-1989
JultoOct1980 <- NSDQmth %>% 
  filter(month %in% c(7:10),
         decade == "1980-1989") 

NovtoJun1980 <- NSDQmth %>% 
  filter(month %in% c(1:6, 11, 12),
         decade == "1980-1989")

test1980 <- t.test(NovtoJun1980$perc_close, JultoOct1980$perc_close, alternative = "less")

# 1970-1979
JultoOct1970 <- NSDQmth %>% 
  filter(month %in% c(7:10),
         decade == "1970-1979") 

NovtoJun1970 <- NSDQmth %>% 
  filter(month %in% c(1:6, 11, 12),
         decade == "1970-1979")

test1970 <- t.test(NovtoJun1970$perc_close, JultoOct1970$perc_close, alternative = "less")


# Summary of all p-values

pvalues <- rbind(test1970$p.value, test1980$p.value, test1990$p.value, test2000$p.value, test2010$p.value, testall$p.value)

labels <- append(as.vector(unique(NSDQmth$decade)), "All")

data.frame("decade" = labels, pvalues)
```

General guidelines:
1. Turn the variable that we are going to loop into a number (eg: decade_code)
2. Initialize the vector we want to store in BEFORE the loop begins
3. Check that you are storing only a single element (eg: not a data frame or vector, because this would produce a list)
4. Store into the vector in step 2, using [i] to place in each element of the vector.

```{r}
# Testing for loop for t-test

pval <- vector("numeric", 5L)

for(i in 1:5){
  w <- NSDQmth %>% 
  filter(month %in% c(7:10),
         decade_code == i)
  
  x <- NSDQmth %>% 
  filter(month %in% c(1:6, 11, 12),
         decade_code == i)
  
  y <- t.test(x$perc_close, w$perc_close, alternative = "less")
  
  pval[i] <- y$p.value
}

pval <- pval %>% 
  append(testall$p.value)

labels <- append(as.vector(unique(NSDQmth$decade)), "All")

data.frame("decade" = labels, pvalues)
```




